Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-11-15 Arxiv/main.tex
update accuracy plots.
update plots of accuracy

\subsection{Accuracy Evaluation}
\subsubsection{Theoretical Results}

\begin{figure}
\begin{center}
\centering
  \subfigure[2 dimensions with data size $600$]{
    \includegraphics[width=0.4\textwidth]{theory_2d.eps}
  \label{subfig_theory_2d}
  }
  \subfigure[3 dimensions with data size $600$]{
    \includegraphics[width=0.4\textwidth]{theory_3d.eps}
  \label{subfig_theory_3d}
  }
\caption{The theory probabilities of candidates in three mechanisms, with balanced data set and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$ }
\label{fig_theory}
\end{center}
\end{figure}
In Fig. \ref{fig_theory} we plot on the x-axis the Hellinger distance from the true posterior and on the y-axis the theoretical probabilities of outputting the candidates with that distance under the different mechanisms. We consider \emph{balanced} data sets, which means that in the Beta-Binomial model (Figure \ref{subfig_theory_2d}) the datasets will consist of 50\% 1s and the rest 0s, while for the
Dirichelet-Multinomial (Figure  \ref{subfig_theory_3d})
the data will be split in the $k=3$ bins with perecentages of: 33\%, 33\% and 34\% in 3 dimensionality. Same concept in 4 dimensionality.

@@

@@

In this section, we evaluate the accuracy of the mechanisms defined in
Section (\ref{sec_mechs}) w.r.t. four variables, including data size, dimensions,
data variance, prior distribution, and some combinations thereof.
Every plot is an average over 1000 runs. In all the experiments we set
$\epsilon = 1.0$, and $\delta = 10^{-8}$.

@@

\begin{figure}
\begin{center}
\centering
    \includegraphics[width=0.8\textwidth]{sampling_2d.eps}
\caption{Increasing data size with prior $\betad(1,1)$, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$}
\label{fig_vs_datasize_2d}
\end{center}
\end{figure}

\begin{figure}[ht]
\begin{center}
\centering
\subfigure[Increasing data size with $\dirichlet(1,1,1)$ prior distribution, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$]
{
        \includegraphics[width=0.45\textwidth]{sampling_3d.eps} 
        \label{fig_vs_datasize_3d}
}
\subfigure[Increasing data size with $\dirichlet(1,1,1,1)$ prior distribution, Unbalanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$]
{
     \includegraphics[width=0.45\textwidth]{sampling_4d.eps} 
\label{fig_vs_datasize_4d}
}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\centering
    \includegraphics[width=0.6\textwidth]{privacyloss.eps}
\caption{Concrete privacy calculation under settings that: prior distribution:$[1,1]$, $\epsilon = 1.0$ and observed data are uniformly distributed}
\label{fig_privacy}
\end{center}
\end{figure}

>>>>

\subsection{Accuracy Evaluation}
\subsubsection{Theoretical Results}
In Fig. \ref{fig_theory} and \ref{fig_theory_epsilon}, we plot on the x-axis the Hellinger distance from the true posterior and on the y-axis the theoretical probabilities of outputting the candidates with that distance under the different mechanisms. We consider \emph{balanced} data sets, which means that in the Beta-Binomial model (Figure \ref{subfig_theory_2d}) the datasets will consist of 50\% 1s and the rest 0s, while for the
Dirichelet-Multinomial (Figure  \ref{subfig_theory_3d})
the data will be split in the $k=3$ bins with perecentages of: 33\%, 33\% and 34\% in 3 dimensionality. Same concept in 4 dimensionality.

We consider 6 mechanisms in our comparison, including the Laplace mechanism, improved Laplace mechanism, standard exponential mechanism, non-private exponential mechanism (using local sensitivity) and two newly designed mechanisms (one with smooth sensitivity achieving $(\epsilon, \delta)-$dp and the other with $\gamma$ sensitivity achieving $\epsilon-$dp).

\begin{figure}
\begin{center}
\centering
  \subfigure[2 dimensions with data size $600$]{
    \includegraphics[width=0.45\textwidth]{theory_2d.eps}
  \label{subfig_theory_2d}
  }
  \subfigure[3 dimensions with data size $600$]{
    \includegraphics[width=0.45\textwidth]{theory_3d.eps}
  \label{subfig_theory_3d}
  }
\caption{The theory probabilities of outputting candidates in certain distance from true posterior, with balanced data set and parameters $\epsilon = 1.0$}
\label{fig_theory}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\centering
  \subfigure[2 dimensions of data size 1000]{
    \includegraphics[width=0.45\textwidth]{epsilon5_2d_1000.eps}
  \label{subfig_theory_2d}
  }
  \subfigure[2 dimensions of data size 10000]{
    \includegraphics[width=0.45\textwidth]{epsilon5_2d_10000.eps}
  \label{subfig_theory_3d}
  }
\caption{The theory probabilities of outputting candidates in certain distance from true posterior, with balanced data set and parameters $\epsilon = 5.0$}
\label{fig_theory_epsilon}
\end{center}
\end{figure}
Increasing the privacy bound $\epsilon$, we get theoretical results as in Fig. \ref{fig_theory_epsilon}. In 2 dimensions, we can perform better than Laplace mechanisms.

@@

In this section, we evaluate the accuracy of the mechanisms defined in
Section (\ref{sec_mechs}) w.r.t. four variables, including data size, dimensions,
data variance, prior distribution, and some combinations thereof.
Every plot is an average over 1000 runs. In all the experiments we set
$\epsilon = 1.0$.

@@

\begin{figure}
\begin{center}
\centering
    \includegraphics[width=0.8\textwidth]{sampling_2d.eps}
\caption{Increasing data size with prior $\betad(1,1)$, balanced datasets and parameters $\epsilon = 1.0$}
\label{fig_vs_datasize_2d}
\end{center}
\end{figure}

\begin{figure}[ht]
\begin{center}
\centering
\subfigure[Increasing data size with $\dirichlet(1,1,1)$ prior distribution, balanced datasets and parameters $\epsilon = 1.0$]
{
        \includegraphics[width=0.45\textwidth]{sampling_3d.eps} 
        \label{fig_vs_datasize_3d}
}
\subfigure[Increasing data size with $\dirichlet(1,1,1,1)$ prior distribution, balanced datasets and parameters $\epsilon = 1.0$]
{
     \includegraphics[width=0.45\textwidth]{sampling_4d.eps} 
\label{fig_vs_datasize_4d}
}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\centering
    \includegraphics[width=0.6\textwidth]{privacyloss.eps}
\caption{Actual privacy loss of different data size when privacy bound $\epsilon = 1.0$ in 2 dimensions, prior:$\betad(1,1)$ and balanced data}
\label{fig_privacy}
\end{center}
\end{figure}
